---
title: "Amarillo City"
---

## Setup

```{r}

library(tidyverse)
library(janitor)
library(readxl)
library(lubridate)
```

## Import Excel Sheet

First, we will start with Amarillo City data to test out the process. 

```{r amarillo-read}
amarillo <- read_excel("data-raw/AmarilloCity.xlsx")

amarillo
```

It worked! read_excel() is the best!

## Clean up columns

Now I want to clean up the columns so the date and times are separate and there is no extra columns. 
First change the date/time to a date type.

```{r chanage-date}
amarillo_date <- amarillo |> mutate (
  datetime_arrest = mdy_hm(datetime_arrest)
)

amarillo_date |> glimpse()
```

Done!

Now I want to get rid of the Incident #'s column and make the date and time separate columns.

```{r}
amarillo_clean <- amarillo_date |>  mutate(
  date_arrest = date(datetime_arrest)) |> select(
  -'Incident #s') |> cbind(
    age = NA, race = NA, sex = NA, agency_arrest = NA,  ethnicity = NA)

amarillo_clean |> glimpse()

```

How do I get the date separated??? Try pasting the separate pieces together. 



## Export

```{r}
amarillo_clean |> write_csv("data-processed/Amarillo-City.csv")
```






