---
title: "Analysis v2"
---

## Setup

```{r}

library(tidyverse)
library(janitor)
library(clipr)

```

## Import and Combine

We will use list.files(), map() and list_rbind() to import and combine our files in one fell swoop. 

First I am making a list of all my files from the data processed folder. 

```{r}
wx_files_list <- list.files(
  "data-processed",
  pattern = "\\.csv",
  full.names = TRUE
)

wx_files_list
```

Now I am going to combine all the files into one tibble using rbind.

```{r}
wx_all <- wx_files_list |> 
  set_names(basename) |> #what does this do?
  map(
  read_csv, 
  col_select = c(name, charges, address_arrest, age, race, sex, agency_arrest, date_arrest, ethnicity)
  )|> 
    list_rbind(names_to = "source") |> #names_to gives me a column with the source file so I can parse it later
    clean_names()

wx_all
```

Now I am going to break up the source column so I have a column with the city or county name and if it's a city or county, and I will make the date_arrest column a date type. 

```{r}
all_data <- wx_all |> mutate(
  city_county_name = str_split_i(source, "-", 1),
  city_county1 = str_split_i(source,"-", -1),
  city_county = if_else(city_county1 == "City.csv", "City", "County"),
  date_arrest = date(date_arrest)
  ) |> select(-city_county1, -source)

all_data
```

## Analysis

Now we get to do the analysis of all the data together. First, I am going to group by each month. 

```{r}
all_data_month <- all_data |> group_by(month = floor_date(date_arrest, 'month')) |> 
  summarize(arrests = n())

all_data_month

```

Now I want to graph this. 

```{r}
all_data_month |> 
  ggplot(aes(x = month, y = arrests)) +
  geom_point() 
```

```{r}
all_data_region <- all_data |> group_by(city_county_name, date_arrest) |> 
  summarize(arrests = n())

all_data_region
```

```{r}
all_data_region |> 
  ggplot(aes(x = date_arrest, y = arrests)) +
  geom_point(size = 0.25) +
  ylim(0,20) +
  facet_wrap(~city_county_name)
  
```




